---
title: "posts-modeling"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(stm)
```


```{r}
data <- read.csv("alzconnected-data/test_2forum.csv")
processed <- textProcessor(data$p_content, metadata = data)
out <- prepDocuments(processed$documents, processed$vocab, processed$meta) 
docs <- out$documents
vocab <- out$vocab
meta <-out$meta
```

```{r}
fit <- stm(documents = out$documents, vocab = out$vocab, K = 10, data = out$meta, content =~ fid, prevalence =~ s(year)+ fid)
```

```{r}
sageLabels(fit)
plot(fit)
```

## topic metadata relationship
Topic Words:
 Topic 1: -line, mom, poa, child, diagnos, brother, daughter 
 Topic 2: grant, interview, copi, film, unemploy, gregori, award 
 Topic 3: dose, breath, tension, adrenalin, anywayor, fight--flight, peace<U+201D> 
 Topic 4: transform, acknowledg, tree, doesn<U+2019>t, mundan, spiritu, dust 
 Topic 5: degre, estat, clam, atmospher, accus, spousal, manifest 
 Topic 6: bell, affair, run-away, gone, cancer, happi, pray 
 Topic 7: sensit, post, plus, text, feet, toe, report 
 Topic 8: dessert, heater, moon, song, season, holiday, virtual 
 Topic 9: allaudiencesenglishpdf, customiz, samewhatev, task<U+2014>lik, yield, imageri, intro 
 Topic 10: tele-town, covid-, coronavirus, long-term, aarp, code, finder 
 
 Covariate Words:
 Group 461: die, knew, ever, wait, even, end, back 
 Group 2147806999: profess, cognit, button, prefer, accompani, develop, term 
 
 Topic-Covariate Interactions:
 Topic 1, Group 461: buri, ash, grave, flower, hill, cemeteri, funer 
 Topic 1, Group 2147806999: sex, david, teen, suprem, safest, jealous, correspond 
 
 Topic 2, Group 461: jim, knit, articl, flag, govern, recip, factor 
 Topic 2, Group 2147806999: fee, applic, lgbt, queer, averag, chicago, canada 
 
 Topic 3, Group 461: palliat, hip, morphin, rehab, daddi, mama, lung 
 Topic 3, Group 2147806999: tomorrow, staf, version, didn<U+2019>t, impair, dementia-rel, donna 
 
 Topic 4, Group 461: keith, rhoda, psalm, momma, <U+2019>re, dig, deeper 
 Topic 4, Group 2147806999: knit, dishwash, structur, sexual, suprem, pantri, preserv 
 
 Topic 5, Group 461: sweeti, sis, oldest, mum, jerri, garag, empti 
 Topic 5, Group 2147806999: lesbian, sage, latter, transgend, susan, pantri, indic 
 
 Topic 6, Group 461: ash, map, sylvia, insignific, snotti, stong, swift 
 Topic 6, Group 2147806999: reput, fals, element, coverag, perceiv, injustic, transgend 
 
 Topic 7, Group 461: upstair, deb, drawer, size, cloth, donat, scent 
 Topic 7, Group 2147806999: violat, tension, guidelin, tighten, alzconnect, thread, australia 
 
 Topic 8, Group 461: tart, ornament, tree, red, byte, christma, thanksgiv 
 Topic 8, Group 2147806999: indic, bathtub, conserv, bay, hotlin, dream, sister 
 
 Topic 9, Group 461: tape, cake, drug, mama, artist, instructor, song 
 Topic 9, Group 2147806999: frank, archiv, reput, marvel, interact, qualifi, warmest 
 
 Topic 10, Group 461: violat, feedback, thread, mia, pam, impair, simpl 
 Topic 10, Group 2147806999: sage, press, presid, continu, forth, call, beth 
 
```{r}
out$meta$fid <- as.factor(out$meta$fid)
prep <- estimateEffect(1:10 ~ fid + s(year), fit,  meta = out$meta, uncertainty = "Global")
summary(prep, topics=1)
plot(fit, type = "summary", xlim = c(0, .3))
```

```{r}
labelTopics(fit,c(1, 2,3,4,5,6,7,8,9,10))
plot(prep, covariate = "fid", topics = c(1, 2,3,4,5,6,7,8,9,10), model = fit, method = "difference", cov.value1 = "2147806999", cov.value2 = "461", xlab ="LGBT ... Lost", main = "xxx", xlim = c(-.1, .1), labeltype="frex")

```

```{r}
plot(prep,"year", method = "continuous",topic=3, model = fit, printlegend = FALSE)
```

```{r}
plot(fit, type = "perspectives", topics = 2)
```